# 第六章 文本数据分析



## 学习目标 {-}

- 📌 **掌握词汇分析基本方法** 

- 📌 **掌握短语提取基本方法** 

- 📌 **掌握句法分析基本方法** 

- 📌 **掌握语篇分析基本方法** 


```{r message=FALSE}
library(tidyverse)
setwd("~/Nutstore Files/310_Tutorial/LanguageDS-e")
library(quanteda)
#install.packages("readtext")
require(readtext)
library(DT)
library(DiagrammeR)

library(FactoMineR)
library(factoextra)
library(flextable)
library(GGally)
library(ggdendro)
library(igraph)
library(network)
library(Matrix)
library(quanteda.textstats)
library(quanteda.textplots)
library(tm)
library(sna)
library(udpipe)
```

## 语言分析的单位

## 语言分析的维度

## 自然语言处理

### 分词

### 词形还原与词干提取

### 词性标注

### 命名实体识别

### 句法分析

### 语义角色标注

### 语义类别标注

## 语料库量化分析方法

### 词汇分析

#### 高频词分析

#### 关键词分析

#### 共现语境分析

### 短语分析

### 句法分析


### 语篇分析

#### 词汇丰富度分析

#### 文本信息熵

#### 文本可读性

#### 情感分析

#### 计算文体分析


## 课堂任务

### 任务6.1 高频词分析  {-}


```{r eval=F, echo=T}


# quanteda
detectives.raw <- readtext("data/ch6/detectives/*txt")

corps.detectives = corpus(detectives.raw)

summary(corpus(corps.detectives), 5)

docvars(corps.detectives, "book") <- names(corps.detectives)


```


```{r eval=F, echo=T}

# make a dfm

dfm_detectives <- corps.detectives %>%
   tokens(remove_punct = TRUE) %>%
   tokens_remove(stopwords("en")) %>%
   dfm()%>%
   dfm_group(groups = book)

print(dfm_detectives)

topfeatures(dfm_detectives, 20)


```



```{r eval=F, echo=T}

library("quanteda.textstats")
library("quanteda.textplots")

dfm_detectives.freq <- textstat_frequency(dfm_detectives, 
                                          n = 20, 
                                          groups = book)

ggplot(dfm_detectives.freq, 
       aes(x = frequency, y = reorder(feature, frequency))) +
    geom_point() + 
    labs(x = "Frequency", y = "Feature")+
    facet_wrap(~ group, scales = "free") 

```

&emsp;&emsp;我们还可以通过 `tidytext` 包的 `tidy()` 函数，将语料库转换为整洁数据框格式，以便使用 `tidyverse` 工具进一步处理和可视化。

```{r eval=F, echo=T}
tidy.corps.detectives = tidytext::tidy(corps.detectives)%>%
   unnest_tokens(word, text) %>%
   anti_join(stop_words, by = "word")%>%
   group_by(book)%>%
   count(word, sort = TRUE) %>%
   mutate(proportion = n / sum(n)) 

tidy.corps.detectives%>% 
  filter(n > 50) %>%
  ggplot(aes(n, reorder(word, n))) +
  geom_col(fill="#006b7b") +
  facet_wrap(~book, ncol = 3, scales = "free") +
  labs(y = NULL)

```


```{r eval=F, echo=T}
## 计算两者的词汇频率相关性
df.freq = tidy.corps.detectives%>%
 select(-n) %>% 
  pivot_wider(names_from = book, values_from = proportion) %>%
  pivot_longer(`Dee.txt`:`Agatha.txt`,
               names_to = "author", values_to = "proportion")

library(scales)
# expect a warning about rows with missing values being removed
ggplot(df.freq, aes(x = proportion, y = `Sherlock.txt`, 
                      color = abs(`Sherlock.txt` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  theme(legend.position="none") +
   facet_wrap(~author, ncol = 2) +
  labs(y = "Sherlock.txt", x = NULL)

cor.test(data = df.freq[df.freq$author == "Dee.txt",],
         ~ proportion + `Sherlock.txt`)

cor.test(data = df.freq[df.freq$author == "Agatha.txt",],
         ~ proportion + `Sherlock.txt`)

```




### 任务6.2 关键词分析 {-}


#### 使用quanteda自带的函数

```{r eval=F, echo=T}
# Calculate keyness and determine Trump as target group
tstat_keyness <- textstat_keyness(dfm_detectives , 
                                  target = "Dee.txt")

tstat_keyness%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
)

# Plot estimated word keyness
textplot_keyness(tstat_keyness) 
```

#### tidytext
```{r eval=F, echo=T}

texts_df = detectives.raw%>%
  unnest_tokens(word, text)%>%
  mutate(doc_id = dplyr::recode(doc_id , "Dee.txt" = "text1",
                                  "Sherlock.txt" = "text2"))%>%
  group_by(doc_id,word)%>%
  summarise(freq = n())%>%
  spread(doc_id, freq, fill = 0)%>%
  dplyr::rename(token = "word")
  
  
stats_tb2 = texts_df %>%
  dplyr::mutate(text1 = as.numeric(text1),
                text2 = as.numeric(text2)) %>%
  dplyr::mutate(C1 = sum(text1),
                C2 = sum(text2),
                N = C1 + C2) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(R1 = text1+text2,
                R2 = N - R1,
                O11 = text1,
                O12 = R1-O11,
                O21 = C1-O11,
                O22 = C2-O12) %>%
  dplyr::mutate(E11 = (R1 * C1) / N,
                E12 = (R1 * C2) / N,
                E21 = (R2 * C1) / N,
                E22 = (R2 * C2) / N) %>%
  dplyr::select(-text1, -text2)

head(stats_tb2)%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) 


assoc_tb3 = stats_tb2 %>%
  # determine number of rows
  dplyr::mutate(Rws = nrow(.)) %>%   
  # work row-wise
  dplyr::rowwise() %>%
    # calculate fishers' exact test
  dplyr::mutate(p = as.vector(unlist(fisher.test(matrix(c(O11, O12, O21, O22), 
                                                        ncol = 2, byrow = T))[1]))) %>%
# extract descriptives
    dplyr::mutate(ptw_target = O11/C1*1000,
                  ptw_ref = O12/C2*1000) %>%
    
    # extract x2 statistics
    dplyr::mutate(X2 = (O11-E11)^2/E11 + (O12-E12)^2/E12 + (O21-E21)^2/E21 + (O22-E22)^2/E22) %>%
    
    # extract keyness measures
    dplyr::mutate(phi = sqrt((X2 / N)),
                  MI = log2(O11 / E11),
                  t.score = (O11 - E11) / sqrt(O11),
                  PMI = log2( (O11 / N) / ((O11+O12) / N) * 
                                ((O11+O21) / N) ),
                  DeltaP = (O11 / R1) - (O21 / R2),
                  LogOddsRatio = log(((O11 + 0.5) * (O22 + 0.5))  / ( (O12 + 0.5) * (O21 + 0.5) )),
                  G2 = 2 * ((O11+ 0.001) * log((O11+ 0.001) / E11) + (O12+ 0.001) * log((O12+ 0.001) / E12) + O21 * log(O21 / E21) + O22 * log(O22 / E22)),
                  
                  # traditional keyness measures
                  RateRatio = ((O11+ 0.001)/(C1*1000)) / ((O12+ 0.001)/(C2*1000)),
                  RateDifference = (O11/(C1*1000)) - (O12/(C2*1000)),
                  DifferenceCoefficient = RateDifference / sum((O11/(C1*1000)), (O12/(C2*1000))),
                  OddsRatio = ((O11 + 0.5) * (O22 + 0.5))  / ( (O12 + 0.5) * (O21 + 0.5) ),
                  LLR = 2 * (O11 * (log((O11 / E11)))),
                  RDF = abs((O11 / C1) - (O12 / C2)),
                  PDiff = abs(ptw_target - ptw_ref) / ((ptw_target + ptw_ref) / 2) * 100,
                  SignedDKL = sum(ifelse(O11 > 0, O11 * log(O11 / ((O11 + O12) / 2)), 0) - ifelse(O12 > 0, O12 * log(O12 / ((O11 + O12) / 2)), 0))) %>%
    
    # determine Bonferroni corrected significance
    dplyr::mutate(Sig_corrected = dplyr::case_when(p / Rws > .05 ~ "n.s.",
                                                   p / Rws > .01 ~ "p < .05*",
                                                   p / Rws > .001 ~ "p < .01**",
                                                   p / Rws <= .001 ~ "p < .001***",
                                                   T ~ "N.A.")) %>% 
    # round p-value
    dplyr::mutate(p = round(p, 5),
                  type = ifelse(E11 > O11, "antitype", "type"),
                  phi = ifelse(E11 > O11, -phi, phi),
                  G2 = ifelse(E11 > O11, -G2, G2)) %>%
    # filter out non significant results
    dplyr::filter(Sig_corrected != "n.s.") %>%
    # arrange by G2
    dplyr::arrange(-G2) %>%
    # remove superfluous columns
    dplyr::select(-any_of(c("TermCoocFreq", "AllFreq", "NRows", 
                            "R1", "R2", "C1", "C2", "E12", "E21",
                            "E22", "upp", "low", "op", "t.score", "z.score", "Rws"))) %>%
    dplyr::relocate(any_of(c("token", "type", "Sig_corrected", "O11", "O12",
                             "ptw_target", "ptw_ref", "G2",  "RDF", "RateRatio", 
                             "RateDifference", "DifferenceCoefficient", "LLR", "SignedDKL",
                             "PDiff", "LogOddsRatio", "MI", "PMI", "phi", "X2",  
                             "OddsRatio", "DeltaP", "p", "E11", "O21", "O22"))) 
head(assoc_tb3)%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) 


```

### 任务6.3 共现语境分析 {-}


#### 单词语境分析

```{r eval=F, echo=T}
toks_corpus_detectives <- corps.detectives%>%
   tokens(remove_punct = TRUE)%>%
   tokens_remove(stopwords("en")) 

kwic(toks_corpus_detectives , pattern = "murder") %>%
  head()%>%
  as.data.frame()
```

#### 双语平行语料库检索

```{r eval=F, echo=T}
# 导入
law_ce <- read_csv("data/ch6/law.csv",  col_names = TRUE)

# 检索中文
law_ce%>%
  filter(str_detect(cn, "当事人"))%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) # put it at the top of the table


law_ce%>%
  mutate(count = str_count(cn, "当事人"))%>%
  filter(count > 0)

##上下排版的文本如何构建平行语料库

trans_corpus <- read_csv("data/ch6/英汉对照文本.csv",  col_names = FALSE)
row.no = nrow(trans_corpus)

trans.new = trans_corpus%>%
  mutate(key = rep(c("E","C"), (row.no/2)),
         id = rep(1:(row.no/2),each=2))%>%
  spread(key, X1)
trans.new %>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) # put it at the top of the table


#search
trans.new%>%
  filter(str_detect(E, "good"))%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) # put it at the top of the table



```



#### 词汇文本分布 {-}

```{r eval=F, echo=T}
kwic(toks_corpus_detectives , pattern = "murder") %>%
    textplot_xray()

textplot_xray(
    kwic(toks_corpus_detectives, pattern = "murder"),
    kwic(toks_corpus_detectives, pattern = "judge"),
    kwic(toks_corpus_detectives, pattern = "police"),
    scale = "absolute")


```

#### 短语上下文共现 {-}

```{r eval=F, echo=T}
# 对于词组
kwic(toks_corpus_detectives, pattern = phrase("commit crime")) %>%
    head()%>%
   as.data.frame()
```


### 任务6.4 搭配提取 {-}

#### 自带算法
```{r eval=F, echo=T}
toks_corpus_detectives%>%
  #提取包含大写字母的专有名词
    tokens_select(pattern = "^[A-Z]", 
                  valuetype = "regex", 
                  case_insensitive = FALSE, 
                  padding = TRUE) %>%
    textstat_collocations(min_count = 5, 
                          size = 3, 
                          tolower = FALSE)



collocation.3wd <- textstat_collocations(corps.detectives, 
                                         size = 3, 
                                         tolower = FALSE)
```





#### 基于句子提取搭配 {-}

```{r eval=F, echo=T}
# set options
options(stringsAsFactors = F)
options(scipen = 999)
options(max.print=1000)


sentences =corps.detectives%>%
  # split text into sentences
  tokenizers::tokenize_sentences() %>%
  # unlist sentences
  unlist() %>%
  # remove non-word characters
  stringr::str_replace_all("\\W", " ") %>%
  stringr::str_replace_all("[^[:alnum:] ]", " ") %>%
  # remove superfluous white spaces
  stringr::str_squish() %>%
  # convert to lower case and save in 'sentences' object
  tolower() 

head(sentences)

# tokenize the 'sentences' data using quanteda package
coll_basic = sentences %>%
  quanteda::tokens() %>%
  # create a document-feature matrix (dfm) using quanteda
  quanteda::dfm() %>%
  # create a feature co-occurrence matrix (fcm) without considering trigrams
  quanteda::fcm(tri = FALSE)%>%
  # tidy the data using tidytext package
  tidytext::tidy() %>%
  # rearrange columns for better readability
  dplyr::relocate(term, document, count) %>%
  # rename columns for better interpretation
  dplyr::rename(w1 = 1,
                w2 = 2,
                O11 = 3) 

head(coll_basic)%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) 

  # calculate the total number of observations (N)
colldf = coll_basic %>%  
  dplyr::mutate(N = sum(O11)) %>%
  # calculate R1, O12, and R2
  dplyr::group_by(w1) %>%
  dplyr::mutate(R1 = sum(O11),
                O12 = R1 - O11,
                R2 = N - R1) %>%
  dplyr::ungroup(w1) %>%
  # calculate C1, O21, C2, and O22
  dplyr::group_by(w2) %>%
  dplyr::mutate(C1 = sum(O11),
                O21 = C1 - O11,
                C2 = N - C1,
                O22 = R2 - O21) 
head(colldf )%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) 

# reduce and complement data
colldf_redux = colldf %>%
   # determine Term
  dplyr::filter(w1 == "crime",
                # set minimum number of occurrences of w2
                (O11+O21) > 10,
                # set minimum number of co-occurrences of w1 and w2
                O11 > 5)  %>%
  dplyr::rowwise() %>%
  dplyr::mutate(E11 = R1 * C1 / N, 
                E12 = R1 * C2 / N,
                E21 = R2 * C1 / N, 
                E22 = R2 * C2 / N)  
head(colldf_redux )%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) 

assoc_tb = colldf_redux %>%
  # determine number of rows
  dplyr::mutate(Rws = nrow(.)) %>%
    # work row-wise
    dplyr::rowwise() %>%
    # calculate fishers' exact test
    dplyr::mutate(p = as.vector(unlist(fisher.test(matrix(c(O11, O12, O21, O22), 
                                                        ncol = 2, byrow = T))[1]))) %>%
  # extract AM
    # 1. bias towards top left
    dplyr::mutate(btl_O12 = ifelse(C1 > R1, 0, R1-C1),
                  btl_O11 = ifelse(C1 > R1, R1, R1-btl_O12),
                  btl_O21 = ifelse(C1 > R1, C1-R1, C1-btl_O11),
                  btl_O22 = ifelse(C1 > R1, C2, C2-btl_O12),
                  
    # 2. bias towards top right
                  btr_O11 = 0, 
                  btr_O21 = R1,
                  btr_O12 = C1,
                  btr_O22 = C2-R1) %>%
    
    # 3. calculate AM
    dplyr::mutate(upp = btl_O11/R1,
                  low = btr_O11/R1,
                  op = O11/R1) %>%
    dplyr::mutate(AM = op / upp) %>%
    
    # remove superfluous columns
    dplyr::select(-any_of(c("btr_O21", "btr_O12", "btr_O22", "btl_O12", 
                            "btl_O11", "btl_O21", "btl_O22", "btr_O11"))) %>%
    # extract x2 statistics
    dplyr::mutate(X2 = (O11-E11)^2/E11 + (O12-E12)^2/E12 + (O21-E21)^2/E21 + (O22-E22)^2/E22) %>%
    # extract association measures
    dplyr::mutate(phi = sqrt((X2 / N)),
                Dice = (2 * O11) / (R1 + C1),
                LogDice = log((2 * O11) / (R1 + C1)),
                MI = log2(O11 / E11),
                MS = min((O11/C1), (O11/R1)),
                t.score = (O11 - E11) / sqrt(O11),
                z.score = (O11 - E11) / sqrt(E11),
                PMI = log2( (O11 / N) / ((O11+O12) / N) * 
                              ((O11+O21) / N) ),
                DeltaP12 = (O11 / (O11 + O12)) - (O21 / (O21 + O22)),
                DeltaP21 =  (O11 / (O11 + O21)) - (O21 / (O12 + O22)),
                DP = (O11 / R1) - (O21 / R2),
                LogOddsRatio = log(((O11 + 0.5) * (O22 + 0.5))  / ( (O12 + 0.5) * (O21 + 0.5) )),
                # calculate LL aka G2
                G2 = 2 * (O11 * log(O11 / E11) + O12 * log(O12 / E12) + O21 * log(O21 / E21) + O22 * log(O22 / E22))) %>%

  # determine Bonferroni corrected significance
  dplyr::mutate(Sig_corrected = dplyr::case_when(p / Rws > .05 ~ "n.s.",
                                                 p / Rws > .01 ~ "p < .05*",
                                                 p / Rws > .001 ~ "p < .01**",
                                                 p / Rws <= .001 ~ "p < .001***",
                                                 T ~ "N.A.")) %>%
  
  # round p-value
    dplyr::mutate(p = round(p, 5)) %>%
    # filter out non significant results
    dplyr::filter(Sig_corrected != "n.s.",
                # filter out instances where the w1 and w2 repel each other
                E11 < O11) %>%
    # arrange by DeltaP12 (association measure)
    dplyr::arrange(-DeltaP12) %>%
    # remove superfluous columns
    dplyr::select(-any_of(c("TermCoocFreq", "AllFreq", "NRows", "O12", "O21", 
                            "O22", "R1", "R2", "C1", "C2", "E11", "E12", "E21",
                            "E22", "upp", "low", "op", "Rws"))) 

head(assoc_tb)%>%
  datatable(.,
  filter = "top",
  class = 'cell-border stripe hover compact'
) 

```

#### 基于目标词提取搭配 {-}

```{r eval=F, echo=T}

kwic_words <- quanteda::tokens_select(tokens(corps.detectives,
                                             remove_numbers = TRUE, 
                                             remove_punct = TRUE), 
                                      pattern = "kill", 
                                      window = 5, 
                                      selection = "keep") %>%
  unlist() %>%
  # tabulate results
  table() %>%
  # convert into data frame
  as.data.frame() %>%
  # rename columns
  dplyr::rename(token = 1,
                n = 2) %>%
  # add a column with type
  dplyr::mutate(type = "kwic")

corpus_words <- corps.detectives %>%
  # tokenize the corpus files
  quanteda::tokens( remove_numbers = TRUE, 
                    remove_punct = TRUE) %>%
  # unlist the tokens to create a data frame
  unlist() %>%
  as.data.frame() %>%
  # rename the column to 'token'
  dplyr::rename(token = 1) %>%
  # group by 'token' and count the occurrences
  dplyr::group_by(token) %>%
  dplyr::summarise(n = n()) %>%
  # add column stating where the frequency list is 'from'
  dplyr::mutate(type = "corpus")

freq_df <- dplyr::left_join(corpus_words, kwic_words, by = c("token")) %>%
  # rename columns and select relevant columns
  dplyr::rename(corpus = n.x,
                kwic = n.y) %>%
  dplyr::select(-type.x, -type.y) %>%
  # replace NA values with 0 in 'corpus' and 'kwic' columns
  tidyr::replace_na(list(corpus = 0, kwic = 0))



stats_tb = freq_df %>%
  dplyr::filter(corpus > 0) %>%
  dplyr::mutate(corpus = as.numeric(corpus),
                kwic = as.numeric(kwic)) %>%
  dplyr::mutate(corpus= corpus-kwic,
                C1 = sum(kwic),
                C2 = sum(corpus),
                N = C1 + C2) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(R1 = corpus+kwic,
                R2 = N - R1,
                O11 = kwic,
                O12 = R1-O11,
                O21 = C1-O11,
                O22 = C2-O12) %>%
  dplyr::mutate(E11 = (R1 * C1) / N,
                E12 = (R1 * C2) / N,
                E21 = (R2 * C1) / N,
                E22 = (R2 * C2) / N) %>%
  dplyr::select(-corpus, -kwic) 

assoc_tb2 = stats_tb %>%
  # determine number of rows
  dplyr::mutate(Rws = nrow(.)) %>%
    # work row-wise
    dplyr::rowwise() %>%
    # calculate fishers' exact test
    dplyr::mutate(p = as.vector(unlist(fisher.test(matrix(c(O11, O12, O21, O22), 
                                                        ncol = 2, byrow = T))[1]))) %>%

      # extract AM
    # 1. bias towards top left
    dplyr::mutate(btl_O12 = ifelse(C1 > R1, 0, R1-C1),
                  btl_O11 = ifelse(C1 > R1, R1, R1-btl_O12),
                  btl_O21 = ifelse(C1 > R1, C1-R1, C1-btl_O11),
                  btl_O22 = ifelse(C1 > R1, C2, C2-btl_O12),
                  
    # 2. bias towards top right
                  btr_O11 = 0, 
                  btr_O21 = R1,
                  btr_O12 = C1,
                  btr_O22 = C2-R1) %>%
    
    # 3. calculate AM
    dplyr::mutate(upp = btl_O11/R1,
                  low = btr_O11/R1,
                  op = O11/R1) %>%
    dplyr::mutate(AM = op / upp) %>%
    
    # remove superfluous columns
    dplyr::select(-any_of(c("btr_O21", "btr_O12", "btr_O22", "btl_O12", 
                            "btl_O11", "btl_O21", "btl_O22", "btr_O11"))) %>% 
  
    # extract x2 statistics
    dplyr::mutate(X2 = (O11-E11)^2/E11 + (O12-E12)^2/E12 + (O21-E21)^2/E21 + (O22-E22)^2/E22) %>%
    # extract expected frequency
    dplyr::mutate(Exp = E11) %>%

    # extract association measures
    dplyr::mutate(phi = sqrt((X2 / N)),
                MS = min((O11/C1), (O11/R1)),
                Dice = (2 * O11) / (R1 + C1),
                LogDice = log((2 * O11) / (R1 + C1)),
                MI = log2(O11 / E11),
                t.score = (O11 - E11) / sqrt(O11),
                z.score = (O11 - E11) / sqrt(E11),
                PMI = log2( (O11 / N) / ((O11+O12) / N) * 
                              ((O11+O21) / N) ),
                DeltaP12 = (O11 / (O11 + O12)) - (O21 / (O21 + O22)),
                DeltaP21 =  (O11 / (O11 + O21)) - (O21 / (O12 + O22)),
                DP = (O11 / R1) - (O21 / R2),
                LogOddsRatio = log(((O11 + 0.5) * (O22 + 0.5))  / ( (O12 + 0.5) * (O21 + 0.5) )),
                # calculate LL aka G2
                G2 = 2 * (O11 * log(O11 / E11) + O12 * log(O12 / E12) + O21 * log(O21 / E21) + O22 * log(O22 / E22))) %>%
  
  # determine Bonferroni corrected significance
  dplyr::mutate(Sig_corrected = dplyr::case_when(p / Rws > .05 ~ "n.s.",
                                                 p / Rws > .01 ~ "p < .05*",
                                                 p / Rws > .001 ~ "p < .01**",
                                                 p / Rws <= .001 ~ "p < .001***",
                                                 T ~ "N.A.")) %>%  
  
  # round p-value
    dplyr::mutate(p = round(p, 5)) %>%
    # filter out non significant results
    dplyr::filter(Sig_corrected != "n.s.",
                # filter out instances where the w1 and w2 repel each other
                E11 < O11) %>%
    # arrange by phi (association measure)
    dplyr::arrange(-DeltaP12) %>%
    # remove superfluous columns
    dplyr::select(-any_of(c("TermCoocFreq", "AllFreq", "NRows", "O12", "O21", 
                            "O22", "R1", "R2", "C1", "C2", "E11", "E12", "E21",
                            "E22", "upp", "low", "op", "Rws"))) 

```

```{r eval=F, echo=T}
# sort the assoc_tb2 data frame in descending order based on the 'phi' column
assoc_tb2 %>%
  dplyr::arrange(-phi) %>%
  # select the top 20 rows after sorting
  head(20) %>%
  # create a ggplot with 'token' on the x-axis (reordered by 'phi') and 'phi' on the y-axis
  ggplot(aes(x = reorder(token, phi, mean), y = phi)) +
  # add a scatter plot with points representing the 'phi' values
  geom_point() +
  # flip the coordinates to have horizontal points
  coord_flip() +
  # set the theme to a basic white and black theme
  theme_bw() +
  # set the x-axis label to "Token" and y-axis label to "Association strength (phi)"
  labs(x = "Token", y = "Association strength (phi)")
```


```{r eval=F, echo=T}
# sort the assoc_tb2 data frame in descending order based on the 'phi' column
assoc_tb2 %>%
  dplyr::arrange(-phi) %>%
  # select the top 20 rows after sorting
  head(20) %>%
  # create a ggplot with 'token' on the x-axis (reordered by 'phi') and 'phi' on the y-axis
  ggplot(aes(x = reorder(token, phi, mean), y = phi, label = phi)) +
  # add a bar plot using the 'phi' values
  geom_bar(stat = "identity") +
  # add text labels above the bars with rounded 'phi' values
  geom_text(aes(y = phi - 0.005, label = round(phi, 3)), color = "white", size = 3) + 
  # flip the coordinates to have horizontal bars
  coord_flip() +
  # set the theme to a basic white and black theme
  theme_bw() +
  # set the x-axis label to "Token" and y-axis label to "Association strength (phi)"
  labs(x = "Token", y = "Association strength (phi)")
```



```{r eval=F, echo=T}
# sort the assoc_tb2 data frame in descending order based on the 'phi' column
top20colls <- assoc_tb2 %>%
  dplyr::arrange(-phi) %>%
  # select the top 20 rows after sorting
  head(20) %>%
  # extract the 'token' column 
  dplyr::pull(token)
# inspect the top 20 tokens with the highest 'phi' values
top20colls

# tokenize the 'sentences' data using quanteda package
keyword_fcm <- sentences %>%
  quanteda::tokens() %>%
  # create a document-feature matrix (dfm) from the tokens
  quanteda::dfm() %>%
  # select features based on 'top20colls' and the term "selection" pattern
  quanteda::dfm_select(pattern = c(top20colls, "kill")) %>%
  # Create a symmetric feature co-occurrence matrix (fcm) 
  quanteda::fcm(tri = FALSE)

# inspect the first 6 rows and 6 columns of the resulting fcm
keyword_fcm[1:6, 1:6]

# create a hierarchical clustering object using the distance matrix of the fcm as data
hclust(dist(keyword_fcm),     
       # use ward.D as linkage method
       method="ward.D2") %>% 
  # generate visualization (dendrogram)
  ggdendrogram() +              
  # add title
  ggtitle("20 most strongly collocating terms of 'kill'")  

```


```{r eval=F, echo=T}
# create a network plot using the fcm
quanteda.textplots::textplot_network(keyword_fcm,
                                     # set the transparency of edges to 0.8 for visibility
                                     edge_alpha = 0.8,
                                     # set the color of edges to gray
                                     edge_color = "gray",
                                     # set the size of edges to 2 for better visibility
                                     edge_size = 2,
                                     # adjust the size of vertex labels 
                                     # based on the logarithm of row sums of the fcm
                                     vertex_labelsize = log(rowSums(keyword_fcm)))
```



### 任务6.5 依存句法分析 {-}

#### 依存句法标注 {-}

```{r eval=F, echo=T}
#Load the model
# First load the model which you have downloaded or which you have stored somewhere on disk.
# 
# udmodel <- udpipe_download_model(language = "chinese")

## Either give a file in the current working directory
udmodel_eng <- udpipe_load_model(file = "data/ch6/english-ewt-ud-2.5-191206.udpipe")
# udmodel_chn <- udpipe_load_model(file = "chinese-gsd-ud-2.5-191206.udpipe")

# dee.raw <- scan(file="judge_dee/01.txt", 
#                 what="character", 
#                 sep="\n")

dee.raw = detectives.raw %>%
  filter(doc_id == "Dee.txt")
  
dee.depd <- udpipe_annotate(udmodel_eng, x = dee.raw$text)


dee.df <- as.data.frame(dee.depd)

table(dee.df$upos)
```

#### 词性统计 {-}

```{r eval=F, echo=T}
library(lattice)
stats <- txt_freq(dee.df$upos)
stats$key <- factor(stats$key, levels = rev(stats$key))
barchart(key ~ freq, data = stats, col = "cadetblue", 
         main = "UPOS (Universal Parts of Speech)\n frequency of occurrence", 
         xlab = "Freq")
```

#### 依存句法结构 {-}

```{r eval=F, echo=T}
library(textplot)
# generate dependency plot
dplot <- textplot_dependencyparser(filter(dee.df, doc_id == "doc1",
                                                    paragraph_id == 2, 
                                                    sentence_id == 2), size = 3) 
# show plot
dplot
```


```{r eval=F, echo=T}
stats <- subset(dee.df, upos %in% c("NOUN")) 
stats <- udpipe::txt_freq(stats$token)
stats$key <- factor(stats$key, levels = rev(stats$key))
barchart(key ~ freq, data = head(stats, 20), col = "cadetblue", 
         main = "Most occurring nouns", xlab = "Freq")
```

#### 基于词性的搭配提取 {-}

```{r eval=F, echo=T}
## Using RAKE
stats <- keywords_rake(x = dee.df, term = "lemma", group = "doc_id", 
                       relevant = dee.df$upos %in% c("NOUN", "ADJ"))
stats$key <- factor(stats$keyword, levels = rev(stats$keyword))
barchart(key ~ rake, data = head(subset(stats, freq > 3), 20), col = "cadetblue", 
         main = "Keywords identified by RAKE", 
         xlab = "Rake")
```


```{r eval=F, echo=T}
## Using Pointwise Mutual Information Collocations
dee.df$word <- tolower(dee.df$token)
stats <- keywords_collocation(x = dee.df, term = "word", group = "doc_id")
stats$key <- factor(stats$keyword, levels = rev(stats$keyword))
barchart(key ~ pmi, data = head(subset(stats, freq > 3), 20), col = "cadetblue", 
         main = "Keywords identified by PMI Collocation", 
         xlab = "PMI (Pointwise Mutual Information)")
```


```{r eval=F, echo=T}
## Using a sequence of POS tags (noun phrases / verb phrases)
dee.df$phrase_tag <- as_phrasemachine(dee.df$upos, type = "upos")
stats <- keywords_phrases(x = dee.df$phrase_tag, term = tolower(dee.df$token), 
                          pattern = "(A|N)*N(P+D*(A|N)*N)*", 
                          is_regex = TRUE, detailed = FALSE)
stats <- subset(stats, ngram > 1 & freq > 3)
stats$key <- factor(stats$keyword, levels = rev(stats$keyword))
barchart(key ~ freq, data = head(stats, 20), col = "cadetblue", 
         main = "Keywords - simple noun phrases", xlab = "Frequency")




```


```{r eval=F, echo=T}
library(igraph)
library(ggraph)
library(ggplot2)

## Co-occurrences allow to see how words are used either in the same sentence or next to each other. 
# This R package make creating co-occurrence graphs using the relevant Parts of Speech tags as easy as possible.

# Nouns / adjectives used in same sentence

cooc <- cooccurrence(x = subset(dee.df, upos %in% c("NOUN", "ADJ")), 
                     term = "lemma", 
                     group = c("doc_id", "paragraph_id", "sentence_id"))


wordnetwork <- head(cooc, 30)
wordnetwork <- graph_from_data_frame(wordnetwork)

ggraph(wordnetwork, layout = "fr") +
  geom_edge_link(aes(width = cooc, edge_alpha = cooc), edge_colour = "blue") +
  geom_node_text(aes(label = name), col = "darkgreen", size = 4) +
  theme_graph(base_family = "Arial Narrow") +
  theme(legend.position = "none") +
  labs(title = "Cooccurrences within sentence", subtitle = "Nouns & Adjective")
```


```{r eval=F, echo=T}
cooc <- cooccurrence(dee.df$lemma, 
                     relevant = dee.df$upos %in% c("NOUN", "ADJ"), 
                     skipgram = 1)
head(cooc)

wordnetwork <- head(cooc, 15)
wordnetwork <- graph_from_data_frame(wordnetwork)
ggraph(wordnetwork, layout = "fr") +
  geom_edge_link(aes(width = cooc, edge_alpha = cooc)) +
  geom_node_text(aes(label = name), col = "darkgreen", size = 4) +
  theme_graph(base_family = "Arial Narrow") +
  labs(title = "Words following one another", subtitle = "Nouns & Adjective")
```


```{r eval=F, echo=T}
dee.df$id <- unique_identifier(dee.df, fields = c("sentence_id", "doc_id"))
dtm <- subset(dee.df, upos %in% c("NOUN", "ADJ"))
dtm <- document_term_frequencies(dtm, document = "id", term = "lemma")
dtm <- document_term_matrix(dtm)
dtm <- dtm_remove_lowfreq(dtm, minfreq = 5)
termcorrelations <- dtm_cor(dtm)
y <- as_cooccurrence(termcorrelations)
y <- subset(y, term1 < term2 & abs(cooc) > 0.2)
y <- y[order(abs(y$cooc), decreasing = TRUE), ]
head(y)

```


```{r eval=F, echo=T}
## Define the identifier at which we will build a topic model
dee.df$topic_level_id <- unique_identifier(dee.df, fields = c("doc_id", "paragraph_id", "sentence_id"))
## Get a data.frame with 1 row per id/lemma
dtf <- subset(dee.df, upos %in% c("NOUN"))
dtf <- document_term_frequencies(dtf, document = "topic_level_id", term = "lemma")
head(dtf)

## Create a document/term/matrix for building a topic model
dtm <- document_term_matrix(x = dtf)
## Remove words which do not occur that much
dtm_clean <- dtm_remove_lowfreq(dtm, minfreq = 5)
head(dtm_colsums(dtm_clean))
```


```{r eval=F, echo=T}
############################################################

# Use dependency parsing output to get the nominal subject and the adjective of it
stats <- merge(dee.df, dee.df, 
               by.x = c("doc_id", "paragraph_id", "sentence_id", "head_token_id"),
               by.y = c("doc_id", "paragraph_id", "sentence_id", "token_id"),
               all.x = TRUE, all.y = FALSE, 
               suffixes = c("", "_parent"), sort = FALSE)

stats <- subset(stats, dep_rel %in% "nsubj" & upos %in% c("NOUN") & upos_parent %in% c("ADJ"))

stats$term <- paste(stats$lemma_parent, stats$lemma, sep = " ")
stats <- txt_freq(stats$term)

library(wordcloud)
wordcloud(words = stats$key, freq = stats$freq, min.freq = 5, max.words = 100,
          random.order = FALSE, colors = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02"))



```


### 任务6.6 语篇特征分析 {-}

#### 词汇丰富度 {-}


```{r eval=F, echo=T}

lexical.diversity <- textstat_lexdiv(dfm_detectives, measure = "all")

lexical.diversity.df = lexical.diversity%>%
  as.data.frame()%>%
  # mutate(id = 1:n())%>%
  # filter(id >1 )%>%
  select("document","TTR","C","R","K","D","Vm")%>%
  gather("measures", "values", -c("document"))%>%
  mutate(measures = as.factor(measures),
         measures = fct_relevel(measures, "TTR","C","R","K","D","Vm"))

lexical.diversity.df

## 移动窗口词汇丰富度
lexical.mattr <- textstat_lexdiv(tokens(corps.detectives), 
                                 measure = "MATTR", MATTR_window = 500)

lexical.mattr
```

#### 文本可读性 {-}

```{r eval=F, echo=T}
readability <- textstat_readability(corps.detectives, measure = "all")
readability.df = readability %>%
  select("document","ARI","Flesch","FOG",
         "Coleman.Liau.short","Dale.Chall","Spache")%>%
  gather("measures", "values", -c("document"))%>%
  mutate(measures = as.factor(measures),
         measures = fct_relevel(measures, "ARI","Flesch","FOG",
                                "Coleman.Liau.short","Dale.Chall","Spache"))

```

#### 文本信息熵 {-}



```{r eval=F, echo=T}

textstat_entropy(dfm_detectives)

```


#### 文本情感分析 {-}


```{r eval=F, echo=T}

library(dplyr)
library(stringr)
library(tidytext)

tidy_books <- detectives.raw %>%
  unnest_sentences(sentence, text)%>%
  group_by(doc_id) %>%
  mutate(linenumber = row_number()) %>%
  ungroup() %>%
  unnest_tokens(word, sentence)



tidy.sent = tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(doc_id, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

library(ggplot2)

ggplot(tidy.sent , aes(index, sentiment, fill = doc_id)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~doc_id, ncol = 2, scales = "free_x")

# 进一步看看哪些积极或者消极的词
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
   group_by(doc_id) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(doc_id~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)


```




拓展阅读

![Exploring the State of the Union Addresses: A Case Study with cleanNLP](https://cran.r-project.org/web/packages/cleanNLP/vignettes/state-of-union.html)




