---
title: "第九章 机器学习建模基础"
author: Juqiang
date: Sept 27, 2024
output: word_document
---

# 第九章 机器学习建模入门

```{r message=FALSE}

library(tidyverse)
library(languageR)
setwd("~/Nutstore Files/310_Tutorial/LanguageDS-MS")
library(cluster)
#library(factoextra)
library(caTools)
library(e1071)
library(flextable)
library(lattice)
dir.fig = "~/Nutstore Files/310_Tutorial/LanguageDS-MS/fig/ch9/"
library(plotly)
library(ggfortify)

# remove scientific notation
options(scipen=999)


```

## 学习目标 {-}

- 📌 **了解机器学习建模中数据准备过程** 

- 📌 **掌握监督和非监督学习建模** 

- 📌 **掌握模型优化基本方法** 

- 📌 **掌握模型评估基本方法** 



## 数据准备

### 数据划分

### 重采样

### 数据平衡

### 特征工程

#### 因变量特征工程

#### 缺失值

#### 特征筛选

#### 自变量特征工程

## 算法类型

### 监督学习

### 非监督学习

#### 降维

#### 聚类

## 模型优化

## 模型评估

## 建模工具

## 课堂任务

### 任务9.1 降维技术：主成份分析与因子分析{-}

#### 主成分分析 {-}

```{r eval=F, echo=T}

# 数据导入
metrics_SCA <- read_csv("data/ch9/metrics_SCA_novel.CSV")%>%
  mutate(author = str_extract(books, "[A-z]{1,8}_"),
         author = str_remove(author,"_"))%>%
   mutate(across(where(is.numeric), ~ round(.x, digits = 2)))

# prcomp建模
sc.pr = prcomp(metrics_SCA[, -c(1:10, 25)], scale = T, center = T)
# Scree plot
# components
props = round((sc.pr$sdev^2/sum(sc.pr$sdev^2)), 3)
#png(paste(dir.fig, paste("ch9_components",Sys.Date(),"png",sep = "."),sep = ""),
#     units="in", width=5, height=6, res=600)
barplot(props, col = as.numeric(props > 0.05), 
        xlab = "principal components", 
        ylab = "proportion of variance explained") 
abline(h = 0.05)
#dev.off()


```

```{r eval=F, echo=T}

# factor score
novel.fscore = as.data.frame(sc.pr$x[, 1:3])%>%
  mutate(bookname = metrics_SCA$books)%>%
  relocate(bookname)%>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 4)))

# scatter plot
# png(paste(dir.fig, paste("ch9_pca",Sys.Date(),"png",sep = "."),sep = ""), 
#       units="in", width=5, height=6, res=600)
super.sym = trellis.par.get("superpose.symbol")
splom(data.frame(sc.pr$x[,1:3]), 
        groups = metrics_SCA$author, 
        panel = panel.superpose, 
        key = list( title = "English novelists", 
                      text = list(unique(metrics_SCA$author)), 
                      points = list(pch = super.sym$pch[1:5], 
                                      col = super.sym$col[1:5])))
#dev.off()



# write_csv(novel.fscore,
#           file = paste(dir.fig,
#                        paste("novel.fscore",
#                              Sys.Date(),
#                              "csv",
#                              sep = "."),
#                        sep = "") )

```

```{r eval=F, echo=T}

# factor loadings
novel.floadings = as.data.frame(sc.pr$rotation[, 1:3])%>%
  mutate(features = rownames(sc.pr$rotation))%>%
  relocate(features)%>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 4)))

# write_csv(novel.floadings,
#           file = paste(dir.fig,
#                        paste("novel.floadings",
#                              Sys.Date(),
#                              "csv",
#                              sep = "."),
#                        sep = "") )


# biplot

# stats包
# png(paste(dir.fig, paste("ch9_pca_biplot_Stats",Sys.Date(),"png",sep = "."),sep = ""), 
#       units="in", width=5, height=6, res=600)

biplot(sc.pr, scale = 0)

# dev.off()

# ggplot2
library(ggfortify)
# png(paste(dir.fig, paste("ch9_pca_biplot_ggplot2",Sys.Date(),"png",sep = "."),sep = ""), 
#       units="in", width=5, height=6, res=600)

autoplot(sc.pr, data = metrics_SCA, colour = 'author',
              loadings = TRUE, loadings.colour = 'gray',
              loadings.label = TRUE, loadings.label.size = 3)
# dev.off()

# factoextra包
library(factoextra)
# png(paste(dir.fig, paste("ch9_pca_biplot_factoextra",Sys.Date(),"png",sep = "."),sep = ""), 
#       units="in", width=5, height=6, res=600)

fviz_pca_biplot(sc.pr,
                label="var",
                habillage = metrics_SCA$author)

# dev.off()


```


```{r eval=F, echo=T}

# princomp包
sc.prin = princomp(metrics_SCA[, -c(1:10, 25)], cor = TRUE)
names(sc.prin)

### illstrate how to get eigen values 

#Compute the correlation matrix for the dataset
cor_matrix <- cor(metrics_SCA[, -c(1:10, 25)])

# Perform an eigenvalue decomposition of the correlation matrix
eigen_decomp <- eigen(cor_matrix)

# Extract the eigenvalues
eigen_decomp$values

# Extract the eigenvalues and communality
# eigenvalues 
sc.prin$sdev^2

# communality 
apply(sc.prin$loadings^2, 2, sum)

library(psych)
# Perform Varimax rotation on the factor solution
rotated <- psych::faRotate(sc.prin$loadings,"varimax")

#rotated.loadings = as.data.frame(rotated$loadings)
rotated$loadings

```


```{r eval=F, echo=T}

# factor score
novel.princomp.fscore = as.data.frame(sc.prin$scores[, 1:3])%>%
  mutate(bookname = metrics_SCA$books)%>%
  relocate(bookname)%>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 4)))

# write_csv(novel.princomp.fscore,
#           file = paste(dir.fig,
#                        paste("novel.princomp.fscore",
#                              Sys.Date(),
#                              "csv",
#                              sep = "."),
#                        sep = "") )
  
# factor loadings
novel.princomp.floadings = as.data.frame(sc.prin$loadings[, 1:3])%>%
  mutate(features = rownames(sc.prin$loadings))%>%
  relocate(features)%>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 4)))

# write_csv(novel.princomp.floadings,
#           file = paste(dir.fig,
#                        paste("novel.princomp.floadings",
#                              Sys.Date(),
#                              "csv",
#                              sep = "."),
#                        sep = "") )

```

#### 因子分析 {-}

```{r eval=F, echo=T}
# 尝试不同因子个数
fac.3 = factanal(metrics_SCA[, -c(1:10,25)], 
                  factors = 3,
                  scores = "regression")
fac.3 
# fac.4 = factanal(metrics_SCA[, -c(1:10,25)], 
#                   factors = 4,
#                   scores = "regression")
# 
# fac.5 = factanal(metrics_SCA[, -c(1:10,25)], 
#                   factors = 5,
#                   scores = "regression")

loadings = loadings(fac.3) 
plot(loadings, type = "n", xlim = c(-0.4, 1)) 
text(loadings, rownames(loadings), cex = 0.8)



# 尝试不同因子旋转方式
# 默认是正交 varimax
# 斜交
fac.3.rotate = factanal(metrics_SCA[, -c(1:10,25)], 
                  factors = 3,
           rotation = "promax",
                  scores = "regression")
fac.3.rotate

loadings.rot = loadings(fac.3.rotate) 
plot(loadings.rot, type = "n", xlim = c(-0.4, 1)) 
text(loadings.rot, rownames(loadings), cex = 0.8)


# 提取因子分数
# sc.fac.5=factanal(metrics_SCA[, -c(1:10,25)], 
#                   factors = 5,
#                   scores = "regression")
# 
# sc.fac.5$scores
# 
# loadings(sc.fac.5) 
# loadings(sc.fac.4) 
# loadings(sc.fac.3) 


# factor rotation
# sc.fac.rot = factanal(metrics_SCA[, -c(1:10,25)], 
#                    factors = 5, rotation = "promax") 
# 
# loadings.rot = loadings(sc.fac.rot) 
# plot(loadings.rot, type = "n", xlim = c(-0.4, 1)) 
# text(loadings.rot, rownames(loadings)) 
# abline(h = -0.1, col = "darkgrey")


```

```{r eval=F, echo=T, include= F}
# 
# # factor score
# novel.fa.score = as.data.frame(sc.fac$scores)%>%
#   mutate(bookname = metrics_SCA$books)%>%
#   relocate(bookname)%>%
#   mutate(across(where(is.numeric), ~ round(.x, digits = 4)))
# 
# 
# write_csv(novel.fa.score,
#           file = paste(dir.fig,
#                        paste("novel.fa.score",
#                              Sys.Date(),
#                              "csv",
#                              sep = "."),
#                        sep = "") )
# 
# # factor loadings
# novel.fa.loadings = as.data.frame(sc.fac$loadings[, 1:5])%>%
#   mutate(features = rownames(sc.fac$loadings))%>%
#   relocate(features)%>%
#   mutate(across(where(is.numeric), ~ round(.x, digits = 4)))

```

### 任务9.2 降维技术：对应分析与多维尺度分析{-}

#### 对应分析 {-}

```{r eval=F, echo=T}
library(stylo)

# 导入文本数据
style.corpus <- load.corpus(files = "all", 
                            corpus.dir = "data/ch9/fictions",
                            encoding = "UTF-8")


# 对文本进行分词
tokenized.corpus <- txt.to.words.ext(style.corpus, 
                                     preserve.case = TRUE)

# 根据研究目的我们可以设置一个词表去除一些干扰词。比如我们想排除文本中高频专有名词的干扰。
# proper.noun = c("DEE","Judge","Dee","")
# delete.stop.words(tokenized.corpus, stop.words = proper.noun)

# 一些作者研究认为代词对于计算文体风格有干扰，比如如果是一个大女主的小说，那么女性代词就会很多。但是这些不能代表作者风格，只能代表作品风格。
clean.corpus = delete.stop.words(tokenized.corpus,
                                  stop.words = stylo.pronouns(corpus.lang = "English"))

corpus.char.1 <- txt.to.features(clean.corpus, 
                                       ngram.size = 1, 
                                       features = "w")

# 将数据划分成4000个词一份
sliced.corpus.char.1 <- make.samples(corpus.char.1, 
                              sampling = "normal.sampling", 
                              sample.size = 4000)
# 提取词频特征
features1 <- make.frequency.list(sliced.corpus.char.1)

# 制作词频特征表
freqs1 <- make.table.of.frequencies(sliced.corpus.char.1, 
                                   features = features1)


# Culling
# 通过删选，用户可以指定特征在语料库中的出现比例，以决定其是否被纳入分析。在语料库中未达到指定比例的词语将被忽略。
culled.freqs1 <- perform.culling(freqs1, culling.level = 80)

wd.df = as.data.frame(culled.freqs1)
```


```{r eval=F, echo=T}
# correspondence analysis
detect.ca = corres.fnc(wd.df)

summary(detect.ca, head = TRUE)

meta.novel = data.frame(books = rownames(wd.df))%>%
      mutate(author = str_extract(books, "[A-z]{1,8}_"),
         author = str_remove(author,"_"))

#biplot
plot(detect.ca, 
     rlabels = meta.novel$author, 
     rcol = as.numeric(as.factor(meta.novel$author)), 
     rcex = 0.4, 
     extreme = 0.2, ccol = "blue")


# library(Factoshiny)
# result <- Factoshiny(wd.df)

```

#### 多维尺度分析 {-}


```{r eval=F, echo=T}
wd.df.d = dist(wd.df,                 # create distance matrix
               method = "euclidean")  

wd.mds = cmdscale(wd.df.d, k = 3)


df.mds = data.frame(wd.mds, 
                 books = rownames(wd.df))%>%
         mutate(author = str_extract(books, "[A-z]{1,8}_"),
         author = str_remove(author,"_"))

library(ggplot2)
library(plotly)
library(dplyr)
library(stringr)
library(ggrepel)

# 为了方便，数据命名为X1, X2, X3
colnames(df.mds)[1:3] <- c("Dim1", "Dim2", "Dim3")

# 1. 二维散点图（使用前两个维度）
ggplot(df.mds, aes(x = Dim1, y = Dim2, color = author)) +
  geom_point(size = 3, alpha = 0.7) +
  geom_text_repel(aes(label = books), size = 3, max.overlaps = 20) +
  labs(title = "MDS Visualization (2D)",
       x = "Dimension 1",
       y = "Dimension 2",
       color = "Author") +
  theme_minimal() +
  theme(legend.position = "right")

# 2. 按作者分面的二维图
ggplot(df.mds, aes(x = Dim1, y = Dim2, color = author)) +
  geom_point(size = 3) +
  geom_text_repel(aes(label = books), size = 2.5, max.overlaps = 10) +
  facet_wrap(~ author, scales = "free") +
  labs(title = "MDS Visualization by Author",
       x = "Dimension 1",
       y = "Dimension 2") +
  theme_minimal() +
  theme(legend.position = "none")




```

### 任务9.3 聚类算法 {-}

#### 层次聚类 {-}

```{r eval=F, echo=T}


#### 检测数据是否可以聚类
clusttendency <- get_clust_tendency(wd.df,    
                   # define number of points from sample space
                                    n = 9,      
                   gradient = list(
                     # define color for low values
                     low = "steelblue",
                     # define color for high values
                     high = "white")) 

clusttendency[1]

```


```{r eval=F, echo=T}
#### 数据预处理
wd.dfs <- scale(wd.df)
# 计算距离
clustd <- dist(wd.dfs, method = "euclidean") 
# 创建聚类
cd <- hclust(clustd, method="ward.D2") 
# 距离图           
plot(cd, hang = -1)    
# Display dendrogram with improvements
plot(cd, 
     hang = -1, 
     cex.lab = 0.001,  # Adjust label font size
     las = 2,        # Rotate labels for better readability
     main = "Dendrogram",  # Add title
     col = "blue")   # Optional: color the branches
### 确定最佳的聚类数量
optclus <- sapply(2:8, function(x) summary(silhouette(cutree(cd, k = x), clustd))$avg.width)
optclus # inspect results
# 最佳的聚类数量是具有最高轮廓系数（silhouette width）的聚类方案。我们将树状图剪切为最佳的聚类数量，并绘制结果。
optnclust <- which(optclus == max(optclus)) # determine optimal number of clusters
groups <- cutree(cd, k=optnclust) # cut tree into optimal number of clusters


plot(cd, hang = -1, cex = .75)             # plot result as dendrogram
rect.hclust(cd, k = optnclust, border="red") # draw red borders around clusters

```



```{r eval=F, echo=T}

png(paste(dir.fig, paste("_ch9_cluster",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=5, height=6, res=600)
plot(cd, hang = -1, cex = .75)             # plot result as dendrogram
rect.hclust(cd, k = optnclust, border="red") # draw red borders around clusters
dev.off()
```



```{r eval=F, echo=T}
  # use euclidean (!) distance

## 计算距离的各种方法
# # create distance matrix (euclidean method: not good when dealing with many dimensions)
# clustd <- dist(clusts, method = "euclidean")
# # create distance matrix (maximum method: here the difference between points dominates)
# clustd_maximum <- round(dist(clusts, method = "maximum"), 2)
# # create distance matrix (manhattan method: most popular choice)
# clustd_manhatten <- round(dist(clusts, method = "manhattan"), 2) 
# # create distance matrix (canberra method: for count data only - focuses on small differences and neglects larger differences)
# clustd_canberra <- round(dist(clusts, method = "canberra"), 2)
# # create distance matrix (binary method: for binary data only!)
# clustd_binary <- round(dist(clusts, method = "binary"), 2) 
# # create distance matrix (minkowski method: is not a true distance measure)
# clustd_minkowski <- round(dist(clusts, method = "minkowski"), 2) 
# # distance method for words: daisy (other possible distances are "manhattan" and "gower")
# clustd_daisy <- round(daisy(clusts, metric = "euclidean"), 2)
```

```{r eval=F, echo=T}
    

# 创建cluster的方法
# # single linkage: cluster with nearest data point
# cd_single <- hclust(clustd, method="single") 
# # create cluster object (ward.D linkage)
# cd_wardd <- hclust(clustd, method="ward.D")
# # create cluster object (ward.D2 linkage): 
# # cluster in a way to achieve minimum variance
# cd_wardd2 <- hclust(clustd, method="ward.D2")
# # average linkage: cluster with closest mean
# cd_average <- hclust(clustd, method="average") 
# # mcquitty linkage
# cd_mcquitty <- hclust(clustd, method="mcquitty") 
# # median linkage: cluster with closest median
# cd_median <- hclust(clustd, method="median")
# # centroid linkage: cluster with closest prototypical point of target cluster
# cd_centroid <- hclust(clustd, method="centroid") 
# # complete linkage: cluster with nearest/furthest data point of target cluster
# cd_complete <- hclust(clustd, method="complete")  

```



```{r eval=F, echo=T}
# library(pvclust)
# #### 检验分类是否合理， 现在我们将通过使用自助法（bootstrapping）验证聚类解决方案，测试聚类是否合理。
# res.pv <- pvclust(t(wd.dfs),                     # apply pvclust method to clus data
#                   method.dist="euclidean",  # use eucledian distance
#                   method.hclust="ward.D2",  # use ward.d2 linkage
#                   nboot = 100)              # use 100 bootstrap runs
# 
# plot(res.pv, cex = .75)
# pvrect(res.pv)

```

#### 类别型数据聚类分析 {-}

```{r eval=F, echo=T}

tone.phon <- read.csv("data/ch9/tone-phonology.CSV")

row.names(tone.phon)=tone.phon$language
#tone.phon = select(tone.phon, -language)
# convert into factors
tone.phon <- apply(tone.phon, 1, function(x){
  x <- as.factor(x) })
# clean data
tone.phon.mtr  <- t(as.matrix(tone.phon))
# create distance matrix
tone.phon.mtr.d<- dist(tone.phon.mtr[,-1] , method = "binary")   # create a distance object with binary (!) distance
# create cluster object (ward.D2 linkage)   : cluster in a way to achieve minimum variance
tone.phon.mtr.cd <- hclust(tone.phon.mtr.d, method="ward.D2")
# plot result as dendrogram
plot(tone.phon.mtr.cd , hang = -1)              # display dendogram
```

```{r eval=F, echo=T}

png(paste(dir.fig, paste("_ch9_cluster.category",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=5, height=6, res=600)
plot(tone.phon.mtr.cd , hang = -1)              # display dendogram
dev.off()

```

#### 分割优化 {-}

```{r eval=F, echo=T}
# k-means clustering 
km = kmeans(sc.pr$x[,1:3], centers=5, nstart=12)

# Coordinates of individuals
ind.coord <- as.data.frame(get_pca_ind(sc.pr)$coord)
# Add clusters obtained using the K-means algorithm
ind.coord$cluster <- factor(km$cluster)
# Add Species groups from the original data sett
ind.coord$author <- metrics_SCA$author
ind.coord$text <- metrics_SCA$books

# Percentage of variance explained by dimensions
eigenvalue <- round(get_eigenvalue(sc.pr), 1)
variance.percent <- eigenvalue$variance.percent
head(eigenvalue)

library(ggpubr)

ggscatter(ind.coord, x = "Dim.1", y = "Dim.2",
  color = "cluster", 
  palette = "npg", 
  ellipse = TRUE, 
  ellipse.type = "convex",
  label = "text",
  shape = "author", size = 1.5,  legend = "right", 
  ggtheme = theme_bw(),
  xlab = paste0("PC 1 (", variance.percent[1], "% )" ),
  ylab = paste0("PC 2 (", variance.percent[2], "% )" )) 

```


```{r eval=F, echo=T}

png(paste(dir.fig, paste("_ch9_kmeans",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

ggscatter(ind.coord, x = "Dim.1", y = "Dim.2",
  color = "cluster", 
  palette = "npg", 
  ellipse = TRUE, 
  ellipse.type = "convex",
  label = "text",
  shape = "Registers", size = 1.5,  legend = "right", 
  ggtheme = theme_bw(),
  xlab = paste0("PC 1 (", variance.percent[1], "% )" ),
  ylab = paste0("PC 2 (", variance.percent[2], "% )" )) 

dev.off()

```


计算文体学

```{r eval=F, echo=T}
# 主成分分析
stylo(frequencies = culled.freqs1, 
      analysis.type = "PCR",
      custom.graph.title = "Judge Dee and Sherlock", 
      pca.visual.flavour = "technical", 
      write.png.file = TRUE, gui = FALSE)



# 显示两本书在第一第二主成分空间的分布
stylo(frequencies = culled.freqs1, 
      analysis.type = "PCR", 
      mfw.min = 100, mfw.max = 500,
      custom.graph.title = "Judge Dee and Sherlock", 
      write.png.file = FALSE, gui = FALSE)


# 显示不同高频词的权重loadings
stylo(frequencies = culled.freqs1, 
      analysis.type = "PCR", 
      custom.graph.title = "Judge Dee and Sherlock",
      pca.visual.flavour = "loadings", 
      write.png.file = FALSE, 
      gui = FALSE)

# cluster analysis
stylo(frequencies = culled.freqs1, 
      analysis.type = "CA", 
      write.png.file = FALSE,  
      custom.graph.title = "Judge Dee and Sherlock", 
      gui = FALSE)


```


### 任务9.4 监督学习数据集划分 {-}


```{r eval=F, echo=T}
# Helper packages 
library(tidymodels)

pictureNaming <- read_csv("data/ch9/pictureNaming.new.csv")%>%
  filter(AoA_r != "#NULL!")%>%
  drop_na()%>%
  mutate(AoA_r = as.numeric(AoA_r),
         AoA_o = as.numeric(AoA_o))%>%
  select("LEN","VAR","IMG","FAM","VC","FREQ", 
         "NAgree","H_value","CA","AoA_r","AoA_o", "RT_harm")%>%
  mutate(LEN = as.factor(LEN))

# Using base R 
set.seed(123) # for reproducibility  
index_1 <- sample(1:nrow(pictureNaming), round(nrow(pictureNaming) * 0.7)) 
train_1 <- pictureNaming[index_1, ] 
test_1 <- pictureNaming[-index_1, ]  
# Using caret package 
library(caret)
set.seed(123) # for reproducibility  
index_2 <- createDataPartition(pictureNaming$RT_harm, p = 0.7, list = FALSE) 
train_2 <- pictureNaming[index_2, ] 
test_2 <- pictureNaming[-index_2, ]  
# Using rsample package 
library(rsample) # for data splitting  
set.seed(123) # for reproducibility  
split_1 <- initial_split(pictureNaming, prop = 0.7) 
train_3 <- training(split_1) 
test_3 <- testing(split_1)  
# Using h2o package  
# library(h2o) # for resampling and model training  
# h2o set-up 
# h2o.no_progress() # turn off h2o progress bars 
# h2o.init() # launch h2o  
# pictureNaming.h2o <- as.h2o(pictureNaming)
# split_2 <- h2o.splitFrame(pictureNaming, ratios = 0.7, seed = 123) 
# train_4 <- split_2[[1]] 
# test_4 <- split_2[[2]]

# 分层抽样
# orginal response distribution  
table(pictureNaming$LEN) %>% prop.table() 

# stratified sampling with the rsample package 
set.seed(123)  
split_strat <- initial_split(pictureNaming, prop = 0.7, strata = "LEN") 
train_strat <- training(split_strat) 
test_strat <- testing(split_strat)  
# consistent response ratio between train & test 
table(train_strat$LEN) %>% prop.table() 
table(test_strat$LEN) %>% prop.table()


```
### 任务9.5 监督学习缺失数据 {-}

```{r eval=F, echo=T}
pictureNaming.miss <- read_csv("data/ch9/pictureNaming.missing.csv")%>%
  filter(AoA_r != "#NULL!")%>%
  mutate(AoA_r = as.numeric(AoA_r),
         AoA_o = as.numeric(AoA_o))%>%
  select("LEN","VAR","IMG","FAM","VC","FREQ", 
         "NAgree","H_value","CA","AoA_r","AoA_o", "RT_harm")%>%
  mutate(LEN = as.factor(LEN))

sum(is.na(pictureNaming.miss))

pictureNaming.miss %>% 
  is.na() %>%  
  reshape2::melt() %>% 
  ggplot(aes(Var2, Var1, fill=value)) + 
  geom_raster() + 
  coord_flip() + 
  scale_y_continuous(NULL, expand = c(0, 0)) + 
  scale_fill_grey(name = "",  labels = c("Present", "Missing")) + 
  xlab("Observation") + 
  theme(axis.text.y = element_text(size = 4))


# 
pictureNaming.recipe <- recipe(RT_harm ~ ., data = pictureNaming_train) %>%
  step_medianimpute(H_value)%>%
  # step_knnimpute(all_predictors(), neighbors = 6)
  # step_bagimpute(all_predictors()) # tree-based

```

### 任务9.6 监督学习特征工程 {-}
```{r eval=F, echo=T}

# 删除零方差变量
caret::nearZeroVar(pictureNaming, saveMetrics= TRUE) %>% 
  rownames_to_column() %>% 
  filter(nzv)

# 数据分布正态化

# Normalize all numeric columns  
pictureNaming.recipe = recipe(RT_harm ~ ., data = pictureNaming_train) %>% 
  step_YeoJohnson(all_numeric())

# 均值和方差标准化 same mean and variance
pictureNaming.recipe %>%  
  step_center(all_numeric(), -all_outcomes()) %>% 
  step_scale(all_numeric(), -all_outcomes())

# 整合在一起
pictureNaming_split <- initial_split(pictureNaming, prop = 0.7) 
pictureNaming_train <- training(pictureNaming_split) 
pictureNaming_test <- testing(pictureNaming_split)

blueprint <- recipe(RT_harm ~ ., data = pictureNaming_train) %>% 
  step_nzv(all_nominal()) %>% 
  step_center(all_numeric(), -all_outcomes()) %>% 
  step_scale(all_numeric(), -all_outcomes()) %>% 
  step_pca(all_numeric(), -all_outcomes())%>%
  step_dummy(all_nominal(), -all_outcomes(), one_hot = TRUE)

prepare <- prep(blueprint, training = pictureNaming_train)

baked_train <- bake(prepare, new_data = pictureNaming_train) 
baked_test <- bake(prepare, new_data = pictureNaming_test)



```


### 任务9.5 监督学习回归任务 {-}

```{r eval=F, echo=T}
# Modeling packages 
library(rpart) # direct engine for decision tree application 
library(caret) # meta engine for decision tree application  
# Model interpretability packages 
library(rpart.plot) # for plotting decision trees 
library(vip) # for feature importance 
library(pdp) # for feature effects

# 数据分为训练集和测试集
pictureNaming_split <- initial_split(pictureNaming, prop = 0.7) 
pictureNaming_train <- training(pictureNaming_split) 
pictureNaming_test <- testing(pictureNaming_split)



pictureNaming_m1 <- rpart(formula = RT_harm ~ ., 
                          data = pictureNaming_train, method = "anova" )


rpart.plot(pictureNaming_m1)

plotcp(pictureNaming_m1)

# rpart cross validation results 
pictureNaming_m1$cptable

# 不同特征的重要性
vip(pictureNaming_m1, num_features = 7, bar = FALSE)

# 1. 使用模型进行预测
test_predictions <- predict(pictureNaming_m1, newdata = pictureNaming_test)

# 2. 获取测试集真实值
test_actual <- pictureNaming_test$RT_harm

# 3. 创建结果数据框
results <- data.frame(
  Actual = test_actual,
  Predicted = test_predictions,
  Residual = test_actual - test_predictions
)

library(Metrics)      # 评估指标
# 基础回归评估指标
model_performance <- data.frame(
  # 1. 误差指标
  MAE = mae(test_actual, test_predictions),          # 平均绝对误差
  RMSE = rmse(test_actual, test_predictions),        # 均方根误差
  MAPE = mape(test_actual, test_predictions) * 100,  # 平均绝对百分比误差
  
  # 2. 拟合优度指标
  R_squared = cor(test_actual, test_predictions)^2,  # R平方
  Adjusted_R2 = 1 - (1 - cor(test_actual, test_predictions)^2) * 
    (nrow(pictureNaming_test) - 1) / 
    (nrow(pictureNaming_test) - ncol(pictureNaming_test) - 1),
  
  # 3. 相对指标
  NRMSE = rmse(test_actual, test_predictions) / mean(test_actual),  # 标准化RMSE
  
  # 4. 样本统计
  Sample_Size = nrow(pictureNaming_test),
  Predictor_Count = ncol(pictureNaming_test) - 1  # 减去因变量
)

```




```{r eval=F, echo=T}
# 模型优化
pictureNaming_m2 <- rpart( formula = RT_harm ~ ., 
                   data = pictureNaming_train, method = "anova", 
                   control = list(cp = 0, xval = 10) )

rpart.plot(pictureNaming_m2)

plotcp(pictureNaming_m2)

# caret cross validation results 

pictureNaming_m3 <- train(RT_harm ~ ., 
                   data = pictureNaming_train, 
                   method = "rpart", 
                   trControl = trainControl(method = "cv", number = 10), 
                   tuneLength = 20 )  

ggplot(pictureNaming_m3)

vip(pictureNaming_m3, num_features = 7, bar = FALSE)


```

### 任务9.5 监督学习分类任务 {-}

```{r eval=F, echo=T}

# 美国英语本族语者数据
datasetAE <- read_csv("data/ch9/datasetAE.CSV")
datasetAE$focus_type = as.factor(datasetAE$focus_type)
# Create training (70%) and test (30%) sets 

# orginal response distribution  
table(datasetAE$focus_type) %>% prop.table() 

# stratified sampling with the rsample package
datasetAE_split <- initial_split(datasetAE, prop = 0.7, strata = "focus_type") 
datasetAE_train <- training(datasetAE_split) 
datasetAE_test <- testing(datasetAE_split)

table(datasetAE_train$focus_type) %>% prop.table() 
table(datasetAE_test$focus_type) %>% prop.table()

```


#### 决策树模型

```{r eval=F, echo=T}

## model 1
datasetAE.tree1 <- rpart(formula = focus_type ~ ., 
                         data = datasetAE_train)

rpart.plot(datasetAE.tree1)

plotcp(datasetAE.tree1)

# model2
datasetAE.tree2 <- rpart( formula = focus_type ~ ., 
                         data = datasetAE_train,
                         control = list(cp = 0, xval = 4) )
rpart.plot(datasetAE.tree2)
plotcp(datasetAE.tree2)

# model 3
# caret cross validation results 
datasetAE.tree3 <- train( focus_type ~ ., 
                          data = datasetAE_train,
                          method = "rpart", 
                   trControl = trainControl(method = "cv", number = 10), 
                   tuneLength = 20 )  

ggplot(datasetAE.tree3)

# feature importance
vip(datasetAE.tree3, num_features = 21, bar = FALSE)

# Construct partial dependence plots  
# p1 <- partial(datasetAE.tree3, pred.var = "Fallexc") %>% autoplot() 
# p2 <- partial(datasetAE.tree3, pred.var = "Falldur") %>% autoplot() 
# p3 <- partial(datasetAE.tree3, pred.var = c("Fallexc", "Falldur")) %>% 
# 
# plotPartial(levelplot = FALSE, zlab ="yhat", 
#               drape = TRUE, colorkey = TRUE, 
#               screen = list(z = -20, x = -60))  
# # Display plots side by side  
# gridExtra::grid.arrange(p1, p2, p3, ncol = 3)


```


```{r eval=F, echo=T}

png(paste(dir.fig, paste("_ch9_datasetAE.tree1",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

rpart.plot(datasetAE.tree1)

dev.off()

png(paste(dir.fig, paste("_ch9_plotcp_datasetAE.tree1",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

plotcp(datasetAE.tree1)

dev.off()

png(paste(dir.fig, paste("_ch9_datasetAE.tree2",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

rpart.plot(datasetAE.tree1)

dev.off()

png(paste(dir.fig, paste("_ch9_plotcp_datasetAE.tree3",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

plotcp(datasetAE.tree1)

dev.off()

png(paste(dir.fig, paste("_ch9_datasetAE.tree3",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

ggplot(datasetAE.tree3)
dev.off()
# feature importance
png(paste(dir.fig, paste("_ch9_datasetAE.tree3.importance",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

vip(datasetAE.tree3, num_features = 21, bar = FALSE)
dev.off()
```



#### bagging  {-}

```{r eval=F, echo=T}
library(ipred) # for fitting bagged decision trees

# make bootstrapping reproducible 
set.seed(123)  
# train bagged model 
datasetAE_bag1 <- bagging( formula = focus_type ~ ., data = datasetAE_train, 
                           nbagg = 100, coob = TRUE, 
                           control = rpart.control(minsplit = 2, cp = 0) )


```

#### random forest  {-}

```{r eval=F, echo=T}
# Modeling packages 

# Helper packages 
library(dplyr) # for data wrangling 
library(ggplot2) # for awesome graphics  
# Modeling packages 
library(ranger) # a c++ implementation of random forest 
library(h2o) # a java-based implementation of random forest

## package 1
library(randomForest)

set.seed(123)

RF_AE = randomForest(focus_type ~ .,
                    ntree = 500, 
                    data = datasetAE_train, 
                    importance = TRUE)
importance(RF_AE)   

varImpPlot(RF_AE, n.var= 5, main ="AE")

# 在构建随机森林的过程中，每棵决策树都是通过对原始训练数据进行有放回抽样（Bootstrap Sampling）得到的子样本训练出来的。剩下样本则没有被该树用于训练，这些样本就是袋外样本。利用那些没有进行训练的数据来进行预测。

as.data.frame(RF_AE$confusion)%>%
mutate(across(where(is.numeric), ~ round(.x, digits = 2)))%>%
  flextable()%>%
  set_caption(caption = "Table x .")
```


```{r eval=F, echo=T}
## ranger package
library(ranger) # a c++ implementation of random forest 
# number of features  
n_features <- length(setdiff(names(datasetAE_train), "focus_type"))  

# train a default random forest model 
datasetAE_rf1 <- ranger( focus_type ~ ., data = datasetAE_train, 
                    mtry = floor(n_features / 3), 
                    respect.unordered.factors = "order",
                    seed = 123 )  
# get OOB RMSE  
default_rmse <- sqrt(datasetAE_rf1$prediction.error)
# create hyperparameter grid 
hyper_grid <- expand.grid( mtry = floor(n_features * c(.05, .15, .25, .333, .4)), 
                           min.node.size = c(1, 3, 5, 10), 
                           replace = c(TRUE, FALSE), 
                           sample.fraction = c(.5, .63, .8), rmse = NA )  

# execute full cartesian grid search 
for(i in seq_len(nrow(hyper_grid))) {  
  # fit model for ith hyperparameter combination 
fit <- ranger(  formula = focus_type ~ ., 
                  data = datasetAE_train, 
                  num.trees = n_features * 10, 
                  mtry = hyper_grid$mtry[i], 
                  min.node.size = hyper_grid$min.node.size[i], 
                  replace = hyper_grid$replace[i], 
                  sample.fraction = hyper_grid$sample.fraction[i], 
                  verbose = FALSE, seed = 123, respect.unordered.factors = "order", )  
  # export OOB error  
hyper_grid$rmse[i] <- sqrt(fit$prediction.error) 
  }
 
# assess top 10 models 
hyper_grid %>%  
  arrange(rmse) %>%  
  mutate(perc_gain = (default_rmse - rmse) / default_rmse * 100) %>% 
  head(10)%>% mutate(across(where(is.numeric), ~ round(.x, digits = 2)))%>%
  flextable()%>%
  set_caption(caption = "Table x .")

# re-run model with impurity-based variable importance
rf_impurity <- ranger(
  formula = focus_type ~ ., 
  data = datasetAE_train, 
  num.trees = 2000,
  mtry = 20,
  min.node.size = 1,
  sample.fraction = .80,
  replace = FALSE,
  importance = "impurity",
  respect.unordered.factors = "order",
  verbose = FALSE,
  seed  = 123
)

# re-run model with permutation-based variable importance
rf_permutation <- ranger(
  formula = focus_type ~ ., 
  data = datasetAE_train, 
  num.trees = 2000,
  mtry = 20,
  min.node.size = 1,
  sample.fraction = .80,
  replace = FALSE,
  importance = "permutation",
  respect.unordered.factors = "order",
  verbose = FALSE,
  seed  = 123
)

p1 <- vip::vip(rf_impurity, num_features = 25, bar = FALSE)
p2 <- vip::vip(rf_permutation, num_features = 25, bar = FALSE)

gridExtra::grid.arrange(p1, p2, nrow = 1)
```


```{r eval=F, echo=T}
png(paste(dir.fig, paste("_ch9_forest.importance",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=8, height=6, res=600)

p1 <- vip::vip(rf_impurity, num_features = 25, bar = FALSE)
p2 <- vip::vip(rf_permutation, num_features = 25, bar = FALSE)

gridExtra::grid.arrange(p1, p2, nrow = 1)

dev.off()
```




```{r eval=F, echo=T}
# pacakge 3
library(h2o) # a java-based implementation of random forest
h2o.no_progress()
h2o.init(max_mem_size = "5g")

# convert training data to h2o object
train_h2o <- as.h2o(datasetAE_train)

# set the response column to Sale_Price
response <- "focus_type"

# set the predictor names
predictors <- setdiff(colnames(datasetAE_train), response)

h2o_rf1 <- h2o.randomForest(
    x = predictors, 
    y = response,
    training_frame = train_h2o, 
    ntrees = n_features * 10,
    seed = 123
)

h2o_rf1

# hyperparameter grid
# hyper_grid <- list(
#   mtries = floor(n_features * c(.05, .15, .25, .333, .4)),
#   min_rows = c(1, 3, 5, 10),
#   max_depth = c(10, 20, 30),
#   sample_rate = c(.55, .632, .70, .80)
# )

# random grid search strategy
# search_criteria <- list(
#   strategy = "RandomDiscrete",
#   stopping_metric = "mse",
#   stopping_tolerance = 0.001,   # stop if improvement is < 0.1%
#   stopping_rounds = 10,         # over the last 10 models
#   max_runtime_secs = 60*5      # or stop search after 5 min.
# )


# # perform grid search 
# random_grid <- h2o.grid(
#   algorithm = "randomForest",
#   grid_id = "rf_random_grid",
#   x = predictors, 
#   y = response, 
#   training_frame = train_h2o,
#   hyper_params = hyper_grid,
#   ntrees = n_features * 10,
#   seed = 123,
#   stopping_metric = "RMSE",   
#   stopping_rounds = 10,           # stop if last 10 trees added 
#   stopping_tolerance = 0.005,     # don't improve RMSE by 0.5%
#   search_criteria = search_criteria
# )


# collect the results and sort by our model performance metric 
# of choice
# random_grid_perf <- h2o.getGrid(
#   grid_id = "rf_random_grid", 
#   sort_by = "mse", 
#   decreasing = FALSE
# )
# 
# random_grid_perf

```



#### Gradient Boosting  {-}



```{r eval=F, echo=T}
# Modeling packages
library(gbm)      # for original implementation of regular and stochastic GBMs
library(h2o)      # for a java-based implementation of GBM variants
library(xgboost)  # for fitting extreme gradient boosting

h2o.init(max_mem_size = "10g")

train_h2o <- as.h2o(datasetAE_train)
response <- "focus_type"
predictors <- setdiff(colnames(datasetAE_train), response)

# run a basic GBM model
set.seed(123)  # for reproducibility

datasetAE_gbm1 <- gbm(
  formula = focus_type ~ .,
  data = datasetAE_train,
  distribution = "gaussian",  # SSE loss function
  n.trees = 5000,
  shrinkage = 0.1,
  interaction.depth = 3,
  n.minobsinnode = 10,
  cv.folds = 10
)

# find index for number trees with minimum CV error
best <- which.min(datasetAE_gbm1 $cv.error)

# get MSE and compute RMSE
sqrt(datasetAE_gbm1$cv.error[best])

# plot error curve
gbm.perf(datasetAE_gbm1, method = "cv")


# create grid search
hyper_grid <- expand.grid(
  learning_rate = c(0.3, 0.1, 0.05, 0.01, 0.005),
  RMSE = NA,
  trees = NA,
  time = NA
)

# execute grid search
for(i in seq_len(nrow(hyper_grid))) {

  # fit gbm
  set.seed(123)  # for reproducibility
  train_time <- system.time({
    m <- gbm(
      formula = focus_type ~ .,
      data = datasetAE_train,
      distribution = "gaussian",
      n.trees = 5000, 
      shrinkage = hyper_grid$learning_rate[i], 
      interaction.depth = 3, 
      n.minobsinnode = 10,
      cv.folds = 10 
   )
  })
  
  # add SSE, trees, and training time to results
  hyper_grid$RMSE[i]  <- sqrt(min(m$cv.error))
  hyper_grid$trees[i] <- which.min(m$cv.error)
  hyper_grid$Time[i]  <- train_time[["elapsed"]]

}

# results
arrange(hyper_grid, RMSE)

# second try
# search grid
hyper_grid <- expand.grid(
  n.trees = 6000,
  shrinkage = 0.01,
  interaction.depth = c(3, 5, 7),
  n.minobsinnode = c(5, 10, 15)
)

# create model fit function
model_fit <- function(n.trees, shrinkage, interaction.depth, n.minobsinnode) {
  set.seed(123)
  m <- gbm(
    formula = focus_type ~ .,
    data = datasetAE_train,
    distribution = "gaussian",
    n.trees = n.trees,
    shrinkage = shrinkage,
    interaction.depth = interaction.depth,
    n.minobsinnode = n.minobsinnode,
    cv.folds = 10
  )
  # compute RMSE
  sqrt(min(m$cv.error))
}

# perform search grid with functional programming
hyper_grid$rmse <- purrr::pmap_dbl(
  hyper_grid,
  ~ model_fit(
    n.trees = ..1,
    shrinkage = ..2,
    interaction.depth = ..3,
    n.minobsinnode = ..4
    )
)

# results
arrange(hyper_grid, rmse)

# implement a stochastic GBM

# refined hyperparameter grid
hyper_grid <- list(
  sample_rate = c(0.5, 0.75, 1),              # row subsampling
  col_sample_rate = c(0.5, 0.75, 1),          # col subsampling for each split
  col_sample_rate_per_tree = c(0.5, 0.75, 1)  # col subsampling for each tree
)

# random grid search strategy
search_criteria <- list(
  strategy = "RandomDiscrete",
  stopping_metric = "mse",
  stopping_tolerance = 0.001,   
  stopping_rounds = 10,         
  max_runtime_secs = 60*60      
)

# perform grid search 
grid <- h2o.grid(
  algorithm = "gbm",
  grid_id = "gbm_grid",
  x = predictors, 
  y = response,
  training_frame = train_h2o,
  hyper_params = hyper_grid,
  ntrees = 6000,
  learn_rate = 0.01,
  max_depth = 7,
  min_rows = 5,
  nfolds = 10,
  stopping_rounds = 10,
  stopping_tolerance = 0,
  search_criteria = search_criteria,
  seed = 123
)

# collect the results and sort by our model performance metric of choice
grid_perf <- h2o.getGrid(
  grid_id = "gbm_grid", 
  sort_by = "mse", 
  decreasing = FALSE
)

grid_perf


# Grab the model_id for the top model, chosen by cross validation error
best_model_id <- grid_perf@model_ids[[1]]
best_model <- h2o.getModel(best_model_id)

# Now let’s get performance metrics on the best model
h2o.performance(model = best_model, xval = TRUE)

#### XGBoost
library(recipes)
xgb_prep <- recipe(focus_type ~ ., data = datasetAE_train) %>%
  step_integer(all_nominal()) %>%
  prep(training = datasetAE_train, retain = TRUE) %>%
  juice()

X <- as.matrix(xgb_prep[setdiff(names(xgb_prep), "focus_type")])
Y <- xgb_prep$focus_type

set.seed(123)
datasetAE_xgb <- xgb.cv(
  data = X,
  label = Y,
  nrounds = 6000,
  objective = "reg:linear",
  early_stopping_rounds = 50, 
  nfold = 10,
  params = list(
    eta = 0.1,
    max_depth = 3,
    min_child_weight = 3,
    subsample = 0.8,
    colsample_bytree = 1.0),
  verbose = 0
)  

# minimum test CV RMSE
min(datasetAE_xgb$evaluation_log$test_rmse_mean)

# hyperparameter grid
hyper_grid <- expand.grid(
  eta = 0.01,
  max_depth = 3, 
  min_child_weight = 3,
  subsample = 0.5, 
  colsample_bytree = 0.5,
  gamma = c(0, 1, 10, 100, 1000),
  lambda = c(0, 1e-2, 0.1, 1, 100, 1000, 10000),
  alpha = c(0, 1e-2, 0.1, 1, 100, 1000, 10000),
  rmse = 0,          # a place to dump RMSE results
  trees = 0          # a place to dump required number of trees
)

# optimal parameter list
params <- list(
  eta = 0.01,
  max_depth = 3,
  min_child_weight = 3,
  subsample = 0.5,
  colsample_bytree = 0.5
)

# train final model
xgb.fit.final <- xgboost(
  params = params,
  data = X,
  label = Y,
  nrounds = 3944,
  objective = "reg:linear",
  verbose = 0
)

```


#### SVM  {-}

```{r eval=F, echo=T}


svm_AE = svm(formula = focus_type ~ .,
                 data = datasetAE,
                 #regression or classification
                 type = 'C-classification', 
                 kernel = 'radial',
                 cost = "2",
                 cross = 10)

#summary(svm_AE)

svm_AE$tot.accuracy

svm_AE$accuracies

```




```{r eval=F, echo=T}

# Tune an SVM with radial basis kernel 
set.seed(1854) # for reproducibility 
datasetAE_svm <- train( focus_type ~ ., 
                    data = datasetAE_train, 
                    method = "svmRadial", 
                    preProcess = c("center", "scale"), 
                    trControl = trainControl(method = "cv", number = 10), 
                    tuneLength = 10 )

# Plot results  
ggplot(datasetAE_svm ) + 
  theme_light()

as.data.frame(datasetAE_svm$results)%>%
mutate(across(where(is.numeric), ~ round(.x, digits = 2)))%>%
  flextable()%>%
  set_caption(caption = "Table x .")

# Control params for SVM 
ctrl <- trainControl( method = "cv", number = 10, 
                      classProbs = TRUE, 
                      summaryFunction = multiClassSummary # also needed for AUC/ROC 
                      )  
# Tune an SVM 
set.seed(5628) # for reproducibility 
datasetAE_svm_auc <- train( focus_type ~ .,
                        data = datasetAE_train, 
                        method = "svmRadial", 
                        preProcess = c("center", "scale"),  
                        metric = "ROC", # area under ROC curve (AUC)
                        trControl = ctrl, tuneLength = 10 )

confusionMatrix(datasetAE_svm_auc)

# Variable importance plot 
set.seed(2827) # for reproducibility  
# prob_bro <- function(object, newdata) { predict(object, 
#                                                 newdata = newdata, 
#                                                 type = "prob")[, "bro"] }
# vip(datasetAE_svm_auc, 
#     method = "permute", 
#     nsim = 5, 
#     train = datasetAE_train, 
#     target = "focus_type", 
#     metric = "roc_auc", 
#     reference_class = "bro", 
#     pred_wrapper = prob_bro)

vip(
  datasetAE_svm_auc, 
  method = "permute", 
  nsim = 5, 
  train = datasetAE_train, 
  target = "focus_type", 
  metric = yardstick::accuracy_vec, 
  pred_wrapper = function(object, newdata) predict(object, newdata = newdata),
  smaller_is_better = FALSE
)

# vip::list_metrics()
# 
# levels(datasetAE_train$focus_type)



```

```{r eval=F, echo=T}

png(paste(dir.fig, paste("_ch9_datasetAE_svm",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

ggplot(datasetAE_svm ) + 
  theme_light()

dev.off()

png(paste(dir.fig, paste("_ch9_datasetAE_svm_auc_importance",Sys.Date(),"png",sep = "."),sep = ""), 
      units="in", width=6, height=6, res=600)

vip(
  datasetAE_svm_auc, 
  method = "permute", 
  nsim = 5, 
  train = datasetAE_train, 
  target = "focus_type", 
  metric = yardstick::accuracy_vec, 
  pred_wrapper = function(object, newdata) predict(object, newdata = newdata),
  smaller_is_better = FALSE
)

dev.off()


```



```{r eval=F, echo=T}


# 为了模拟美国英语（AE）听众如何感知由中国英语（CE1和CE2）学习者发出的焦点目标词语，使用所有AE数据特征训练了一个支持向量机（SVM）模型，并分别使用两个中国英语学习者组的数据进行测试。
#Cross langauge preception

# 中国英语学习者大一
datasetCE1 = read_csv("data/ch9/datasetCE1.CSV")
# 中国英语学习者大三
datasetCE2 = read_csv("data/ch9/datasetCE2.CSV")
datasetCE1$focus_type = as.factor(datasetCE1$focus_type)
datasetCE2$focus_type = as.factor(datasetCE2$focus_type)



#svm
y_predCE1 = predict(svm_AE, newdata = datasetCE1[-1])
y_predCE2 = predict(svm_AE, newdata = datasetCE2[-1])

library(caret)

conf_ce1 = confusionMatrix(as.factor(datasetCE1$focus_type), y_predCE1)
conf_ce2 = confusionMatrix(as.factor(datasetCE2$focus_type), y_predCE2)

as.data.frame(conf_ce1$table)%>%
  group_by(Reference)%>%
  mutate(accuracy = Freq/sum(Freq),
         LANG = "CE1")%>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 2)))%>%
  flextable()%>%
  set_caption(caption = "Table x CE1.")

as.data.frame(conf_ce2$table)%>%
  group_by(Reference)%>%
  mutate(accuracy = Freq/sum(Freq),
         LANG = "CE2")%>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 2)))%>%
  flextable()%>%
  set_caption(caption = "Table x CE2.")

# 总体准确率在CE1和CE2两组中均高于随机水平，且两组之间的差异较小。在每个组内，BF类词汇相对容易分类，而NF和CF类词汇则较难分类，反映在较低的准确率上。



```



